S2 pioneer factor MS

### 2022-10-14 manuscript/manuscript.Rmd
update config.yaml for motif analysis and outline supp figs

| Reagent                            | Source/vendor            | Catalog/accession \# |
|------------------------------------|--------------------------|----------------------|
| pMT-puro                           | AddGene                  | 17923                |
| Gibson Cloning                     | New England Biolabs      | E2611                |
| Schneider's Medium                 | Thermo Fisher Scientific | 21720001             |
| Fetal Bovine Serum                 | Omega Scientific         | FB-02                |
| Antibiotic/antimycotic             | Thermo Fisher Scientific | 15240062             |
| Effectene Transfection Reagent     | Qiagen                   | 301427               |
| PVDF Membrane                      |                          |                      |
| **Antibodies**                     |                          |                      |
| Anti-Zld                           | Harrison et al., 2010    |                      |
| Anti-Grh                           | Harrison et al., 2010    |                      |
| Anti-Twi                           | He et al., 2015          |                      |
| Anti-HA-peroxidase clone 3F10      | Roche                    | 12013819001          |
| Anti-Tubulin DM1A                  | Sigma                    | T6199-200UL          |
| goat anti-rabbit IgG-HRP conjugate | Bio-Rad                  | 1706515              |
| Anti-HA clone 12CA5                |                          |                      |
|                                    |                          |                      |
|                                    |                          |                      |
|                                    |                          |                      |

@@

@@

>>>>

| Reagent                            | Source/vendor            | Catalog/accession \# |
|------------------------------|-----------------------|-------------------|
| pMT-puro                           | AddGene                  | 17923                |
| Gibson Cloning                     | New England Biolabs      | E2611                |
| Schneider's Medium                 | Thermo Fisher Scientific | 21720001             |
| Fetal Bovine Serum                 | Omega Scientific         | FB-02                |
| Antibiotic/antimycotic             | Thermo Fisher Scientific | 15240062             |
| Effectene Transfection Reagent     | Qiagen                   | 301427               |
| PVDF Membrane                      |                          |                      |
| **Antibodies**                     |                          |                      |
| Anti-Zld                           | Harrison et al., 2010    |                      |
| Anti-Grh                           | Harrison et al., 2010    |                      |
| Anti-Twi                           | He et al., 2015          |                      |
| Anti-HA-peroxidase clone 3F10      | Roche                    | 12013819001          |
| Anti-Tubulin DM1A                  | Sigma                    | T6199-200UL          |
| goat anti-rabbit IgG-HRP conjugate | Bio-Rad                  | 1706515              |
| Anti-HA clone 12CA5                |                          |                      |
|                                    |                          |                      |
|                                    |                          |                      |
|                                    |                          |                      |

@@

**Extended data Figure 1: Generation of stable cell lines.**

@@

**Information to include in supplemental figures:**

-   Schematic of stable cell line generation.

-   Cell line validation by RNA-seq

-   Verification of protein expression.

-   Determination of physiological protein levels.

-   QC for genomics datasets: e.g. PCA, replicate correlation, example genome browsers of individual replicates.

-   Antibody controls: IgG, IPs in WT cells, etc.

-   CUT&RUN time course for Zld and Grh?

-   De novo motif results

-   Analysis of promoter motifs

-   GO analysis for RNA-seq data

-
